Predicting US Presidential Elections

### 2024-11-04 paper/paper.qmd
final

---
title: "Predicting US Presidential Elections"
subtitle: "Analysing Electoral Polls to Model Forecast the Winner of the Upcoming US Presidential Election"
author: 
  - Aamishi Avarsekar
  - Gauravpreet Thind
  - Divya Gupta
thanks: "Code and data are available at: https://github.com/aamishi/marriages_weekly_reflection/tree/master"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

### Outcome Variable
The outcome variable that we decided to focus on is `pct`, which is the proportion of support that a major candidate is projected to receive through that poll. This proportion accounts for the candidate’s support against all other candidates. We use this variable to estimate which candidate is likely to win based on popular vote.
```{r}
# Filter data from July 21, 2024, until today
filtered_data <- kh_data %>%
  filter(end_date >= as.Date("2024-07-21") & end_date <= Sys.Date())

>>>>

---
title: "Predicting US Presidential Elections"
subtitle: "Analysing Electoral Polls to Model Forecast the Winner of the Upcoming US Presidential Election"
author: 
  - Aamishi Avarsekar
  - Gauravpreet Thind
  - Divya Gupta
thanks: "Code and data are available at: https://github.com/aamishi/PredictingUSPresidentialElections"
date: today
date-format: long
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

### Outcome Variable
The outcome variable that we decided to focus on is `pct`, which is the proportion of support that a major candidate is projected to receive through that poll. This proportion accounts for the candidate’s support against all other candidates. We use this variable to estimate which candidate is likely to win based on popular vote.
```{r}
#| include: false
#| warning: false
#| message: false
# Filter data from July 21, 2024, until today
filtered_data <- kh_data %>%
  filter(end_date >= as.Date("2024-07-21") & end_date <= Sys.Date())
